BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-05-01 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd

data <- read.csv('data/test_data.csv', na.strings = "") %>% 
  drop_na(c('Longitude', 'Latitude', 'Date_digital')) %>% 
  unite(col = 'Scientific_name', 
        c(Binomial, Infrarank, Infraspecies), na.rm=TRUE, sep = " ", remove = F) %>% 
  filter(Scientific_name != '')#, Collection_number %in% subs_batch)#, Collection_number %in% subs_batch)

@@

epithet_diff <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(Epithet != POW_Epithet, !Scientific_name %in% genus_mismatch$Scientific_name) %>% 
  select(Collection_number, Scientific_name, Epithet, POW_Genus, POW_Epithet, POW_Infraspecies) %>% 
  distinct(Scientific_name, .keep_all = T) %>%  # do we record repeat collections ?
  mutate(Situation = 
           case_when(
             Collection_number %in% c('1207') ~ 'User Error', 
             Collection_number %in% c(
               '1217', '1251', '1283', '1311', '1337', '1391', '1415', '1421', '1435', '1450', '1576', 
               '1594', '1624', '1627', '1745', '2043', '2086', '2108', '2109', '2120', '2127', '2130', '2135', 
               '2153', '2199', '2227', '2242', '2256', '2289', '2297', '2315', '2343', '2370', '2379', 
               '2393', '2415', '2480', '2511', '2561', '2573', '2648', '2660', 
               '2687', '2690', '2710', '2715', '2727', '2750', '2767', '2818')
             ~ 'Spelling',
             Collection_number %in% c(
               '1556', '1588', '1619', '2445', '2777', '1337', '2004', '2412', '2487', '2748', '2652',
               '2805', '2194', '2040', '2039', '2403', '2328', '2076') 
             ~ 'Outdated', 
             Collection_number %in% c('2644') ~ 'Incorrect',
             Collection_number %in% c(
               '1207', '2326', '2038', '1424', '2618', '2622', '2665', '2711', '2713') 
             ~ 'Internal_Error',
             Collection_number %in% c('2110', '2540') ~ 'Preferred'
           )
  )

>>>>

data <- read.csv('data/test_data.csv', na.strings = "") %>% 
  drop_na(c('Longitude', 'Latitude', 'Date_digital')) %>% 
  unite(col = 'Scientific_name', 
        c(Binomial, Infrarank, Infraspecies), na.rm=TRUE, sep = " ", remove = F) %>% 
  filter(Scientific_name != '', Collection_number %in% subs_batch)#, Collection_number %in% subs_batch)

@@

epithet_diff <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(Epithet != POW_Epithet, !Scientific_name %in% genus_mismatch$Scientific_name) %>% 
  select(Collection_number, Scientific_name, Epithet, POW_Genus, POW_Epithet, POW_Infraspecies) %>% 
  distinct(Scientific_name, .keep_all = T) %>%  # do we record repeat collections ?
  mutate(Situation = 
           case_when(
             Collection_number %in% c('1207') ~ 'User Error', 
             Collection_number %in% c(
               '1217', '1251', '1283', '1311', '1337', '1391', '1415', '1421', '1435', '1450', '1576', 
               '1594', '1624', '1627', '1745', '2043', '2086', '2108', '2109', '2120', '2127', '2130', '2135', 
               '2153', '2199', '2227', '2242', '2256', '2289', '2297', '2315', '2343', '2370', '2379', 
               '2393', '2415', '2480', '2511', '2561', '2573', '2648', '2660', 
               '2687', '2690', '2710', '2715', '2727', '2750', '2767', '2818')
             ~ 'Spelling',
             Collection_number %in% c(
               '1556', '1588', '1619', '2445', '2777', '1337', '2004', '2412', '2487', '2748', '2652',
               '2805', '2194', '2040', '2039', '2252', '2403', '2328', '2076') 
             ~ 'Outdated', 
             Collection_number %in% c('2644') ~ 'Incorrect',
             Collection_number %in% c(
               '1207', '2326', '2038', '1424', '2618', '2622', '2665', '2711', '2713') 
             ~ 'Internal_Error',
             Collection_number %in% c('2110', '2540') ~ 'Preferred'
           )
  )
